# Methods


```{r, label = "MYhistogram", echo = FALSE, fig.cap = "This is where you should write your figure description"}
set.seed(123)
hist(rnorm(10000), xlab = "Your Label Here", col = "red", 
     breaks = "Scott", main = "", freq = FALSE)
```


## Data Collection

## Exploratory Analysis

## Statistical Modeling

```{r}
mod.lm <- lm(Assault ~ UrbanPop, data = USArrests)
anova(mod.lm)
```

Suppose you want the last output in a Table.  See Table \@ref(tab:ANOVA1).

```{r, label = "ANOVA1", echo = FALSE}
knitr::kable(anova(mod.lm), digits = 3, caption = "ANOVA for regressing `Assault` on `UrbanPop`")
```

## Reproducibility

All analyses performed in this paper can be reproduced by running the original `.Rmd` file with RStudio, assuming the link to the original data remains current and the contents thereof remain unchanged. The `R` packages `car` [@R-car], `ggplot2` [@R-ggplot2], `knitr` [@R-knitr], `rmarkdown` [@R-rmarkdown], and `bookdown` [@R-bookdown]  will need to be installed on the user's computer.  Since `bookdown` is being actively developed and is not yet on [CRAN](https://cran.r-project.org/), you will need to install `bookdown` from [GitHub](https://github.com)
by typing the following at the `R` prompt:

```{r, eval = FALSE}
devtools::install_github("rstudio/bookdown")
```
