---
title: "Bare Bones"
author: "Alan Arnholt"
date: '`r format(Sys.time(), "%b %d, %Y")`'
bibliography: PackagesUsed.bib
knit: "bookdown::render_book"
output:
  bookdown::gitbook: default
documentclass: article
link-citations: yes
---

# Introduction

This is an introduction.  See Figure \@ref(fig:MYhistogram) for an example of a density histogram.

# Methods


```{r, label = "MYhistogram", echo = FALSE, fig.cap = "This is where you should write your figure description"}
set.seed(123)
hist(rnorm(10000), xlab = "Your Label Here", col = "red", 
     breaks = "Scott", main = "", freq = FALSE)
```


## Data Collection

## Exploratory Analysis

## Statistical Modeling

```{r}
mod.lm <- lm(Assault ~ UrbanPop, data = USArrests)
anova(mod.lm)
```

Suppose you want the last output in a Table.  See Table \@ref(tab:ANOVA1).

```{r, label = "ANOVA1", echo = FALSE}
knitr::kable(anova(mod.lm), digits = 3, caption = "ANOVA for regressing `Assault` on `UrbanPop`")
```

## Reproducibility

All analyses performed in this paper can be reproduced by running the original `.Rmd` file with RStudio, assuming the link to the original data remains current and the contents thereof remain unchanged. The `R` packages `car` [@R-car], `ggplot2` [@R-ggplot2], `knitr` [@R-knitr], `rmarkdown` [@R-rmarkdown], and `bookdown` [@R-bookdown]  will need to be installed on the user's computer.  Since `bookdown` is being actively developed and is not yet on [CRAN](https://cran.r-project.org/), you will need to install `bookdown` from [GitHub](https://github.com)
by typing the following at the `R` prompt:

```{r, eval = FALSE}
devtools::install_github("rstudio/bookdown")
```

# Results

## Cross Validation

See equation (\@ref(eq:abc)).  See equation (\@ref(eq:ghi)).

\begin{equation}
a^2 + b^2 = c^2
\label{eq:abc}
\end{equation}


\begin{equation}
d^2 + e^2 = f^2
\label{eq:def}
\end{equation}

\begin{equation}
g^2 + h^2 = i^2
\label{eq:ghi}
\end{equation}

## Best Model

# Conclusions

# References
```{r, echo = FALSE, message = FALSE, results = 'hide', warning = FALSE}
PackagesUsed <- c("rmarkdown", "knitr", "base", "xtable", "ggplot2", "car", "bookdown")
# Write bib information
knitr::write_bib(PackagesUsed, file = "PackagesUsed.bib")
# Load packages
lapply(PackagesUsed, library, character.only = TRUE)
```
