---
title: "Bare Bones"
author: "Alan Arnholt"
date: '`r format(Sys.time(), "%b %d, %Y")`'
knit: "bookdown::render_book"
output:
  bookdown::html_document2
link-citations: yes
---

# Introduction

This is an introduction.  See Figure \@ref(fig:MYhistogram) for an example of a density histogram.

# Methods


```{r, label = "MYhistogram", echo = FALSE, fig.cap = "This is where you should write your figure description"}
set.seed(123)
hist(rnorm(10000), xlab = "Your Label Here", col = "red", 
     breaks = "Scott", main = "", freq = FALSE)
```


## Data Collection

## Exploratory Analysis

## Statistical Modeling

```{r}
mod.lm <- lm(Assault ~ UrbanPop, data = USArrests)
anova(mod.lm)
```

Suppose you want the last output in a Table.  See Table \@ref(tab:ANOVA1).

```{r, label = "ANOVA1", echo = FALSE}
knitr::kable(anova(mod.lm), digits = 3, caption = "ANOVA for regressing `Assault` on `UrbanPop`")
```



# Results

## Cross Validation

See equation \@ref(eq:abc).

\begin{equation}
a^2 + b^2 = c^2
\label{eq:abc}
\end{equation}

## Best Model

# Conclusions

# References
